The globular cluster system of the Auriga simulations

### 2019-11-22 response_to_referee.tex

\documentclass{article}

\begin{document}

\section*{General comments about style}
\begin{itemize}
\item
\item
\item
\item
\item I replaced `Sec.' by `Section' to refer to sections in the present work.
Moreover, I changed `Sec.' to `section' to refer to a section in one of the references.
\item All acronyms are introduced the first time they appear in the text
(MW, M31, GC, GCS, YMC, ISM, SN, AGB, DM, and Au). The subset thereof that appears 
in the abstract is also introduced the first time it appears.
\end{itemize}

@@

\section*{Major comments and concerns}
\begin{itemize}
\item Item
\end{itemize}

\section*{Additional major comments}
\begin{itemize}
\item Item
\end{itemize}

\section*{Comments for each section}
\begin{itemize}
\item Item
\end{itemize}

\section*{Minor comments}
\begin{itemize}
\item The indicated typos have been corrected.
\item `missing error bars and references for the virial radii' $\rightarrow$
    I moved the reference from the footnote to the main text.
\item 4.1: `which model do the authors refer to?' $\rightarrow$ 
    added `star formation'.
\item 4.1: `The top half of the left figure' $\rightarrow$ 
    `The top panel of Figure 3'.
\end{itemize}

### 2019-11-22 AurigaGCS.tex
Process feedback referee / Minor comments / first steps

\subsection{Radial distribution}
\label{sec:Rgc}
The bottom panel of Figure~\ref{fig:MW-M31-age-Rgc} shows the radial distribution
of the MW and M31 GCS. We divide the radii of M31 by its virial radius\footnote{
$r_{\text{vir}}$ is the radius in a spherical `top-hat' perturbation model at which
the average density reaches an overdensity of $\Delta_{\text{vir}}=357$ times the 
background density, adopting the values and cosmology from \citet{2017MNRAS.464.3825P}}
$r_{\text{vir,M31}} = 299$~kpc and multiply by $r_{\text{vir,MW}} = 261$~kpc to 
account for the different intrinsic sizes of both galaxies. Values for 
R$_{\text{gal}}$ are readily available in H96e10 (assuming $r_{\odot}=8.0$~kpc), but the galactocentric radius of GCs
in M31 is not available in CR16. Therefore, we follow \citet[][section~4.1]{2019arXiv190111229W} 
to calculate the projected radius $r_{\text{proj}}$ from the observed positions,
adopting M31's central position from the NASA Extragalactic 
Database\footnote{\url{https://ned.ipac.caltech.edu/}} $(\alpha_0, \, \delta_0) =
(0^{\text{h}}42^{\text{m}}44.35^{\text{s}}, \, +41^{\circ}16'08.63")$
and distance $D_{\text{M31}} = 780$~kpc \citep{2005MNRAS.356..979M,2012ApJ...758...11C}.
We calculate $r_{\text{gal}}$ as `average deprojected distance`
$r_{\text{gal}} = r_{\text{proj}} \times (4/\pi)$.

@@

\subsection{Metallicity distribution}
\label{sec:results_FeH}
We investigate whether the model implemented in Auriga produces metallicity 
distributions consistent with the MW and M31 GCSs, and whether
the simulations generate sufficient total mass at metallicities typical for the
MW and M31 GCSs. To visually inspect the former we show the normalized metallicity 
distribution of three specific Auriga galaxies in Figure~\ref{fig:Au4-10and21_FeH}
in comparison to the MW and M31 [Fe/H] distributions.

\begin{figure}
    \includegraphics[width=\columnwidth]{{FeH_obs_Au4-4_Au4-10_Au4-21}.png}
    \caption{
        \emph{Top}: Metallicity distribution of the MW and M31 GCS. The solid 
        purple (magenta) line shows the GCSs of the MW (M31), and we 
        indicate the mean value with an arrow at the bottom of the x-axis. We
        overplot a double Gaussian for the MW GCS using purple dotted lines, taking
        the mean and dispersion from \citep{Harris2001}.
        \emph{Other panels}: three selected Auriga haloes as indicated in the 
        upper right corner. In each of these three panels we show the GG 
        candicates in green, and use a green dotted line for all star particles. 
        We split the GC candidates up into two subpopulations, those that have 
        formed {\it in~situ} (blue), and those that have been accreted (red).
        \label{fig:Au4-10and21_FeH}
    }
\end{figure}
We select \mbox{Au4-10}\footnote{The nomenclature is `Au' for Auriga, followed by the
resolution level (4) and halo number (10, indicating which set of initial
conditions was used).}, \mbox{Au4-21}, and \mbox{Au4-4} to show the
distributions of three individual simulation runs that we consider representative
for specific behaviour, and to highlight that different runs could give rise to 
different distributions. We show the age-selected GC candidates as well as the 
accreted and {\it in~situ} subsets. The top half of the left figure shows the MW 
and M31 GCSs, where we overplot a double Gaussian for the MW GCS by 
adopting literature values of the mean $\mu$ and standard deviation $\sigma$ of 
the metal-rich and metal-poor subpopulations \citep{Harris2001}.

@@

To ease this comparison between the simulations and observations we take the ratio
of the total mass of GC candidates in Auriga to the total GC mass in the MW 
(and M31). We use a diverging colour map centered around the overall median of the 
mass ratio (i.e. we subtract the median of these twenty-five bins from the value 
in each bin). We show this in the top (bottom) panel of Figure~\ref{fig:Au-FeHRgc-ratio}.
Note that the data in the three top right bins is masked because the mass ratio cannot 
be calculated due to zero mass in the observations (therefore the bins are white).
If the product of the bound cluster formation efficiency and consecutive GC 
disruption over a Hubble time would be constant, then the value in each bin would
have been zero. The red and blue bins indicate deviations from such a scenario and
indicate a higher and lower than average mass excess in the simulations. The median 
value used to shift the mass ratio is $2.68$ and $1.69$ dex for the MW and M31, 
respectively. This means that the median `mass budget' that the simulations `can 
afford to lose' is roughly a factor $480$ and $50$ for the MW and M31, respectively. 
The lowest mass surplus for both galaxies is the the bin where $-2.5 <$ [Fe/H] 
$< -1.5$ and $3 < r_{\text{gal}}/\text{kpc} < 8$, for which the simulations produce 
a factor $10^{2.68}/10^{1.33} \approx 22$ and $10^{1.69}/10^{0.75} \approx 9$ 
more mass in GC candidates than what is observed in the MW and M31 respectively.
The highest factor for the MW is $2.1 \times 10^{5}$, and $1.1 \times 10^{3}$
for M31.

@@

Finally, we note that \citet{2006ARA&A..44..193B} compares the number of metal-poor 
GCs to the stellar halo mass and find\footnote{The quantity $T$ is the number of 
GCs per $10^9$ M\Sun \, of galaxy stellar mass.} $T^n_{\text{blue}} \sim 100$, 
while the number of metal-rich GCs compared to the bulge mass yields 
$T^n_{\text{red}} \sim 5$, and therefore conclude that the formation efficiency
of metal-poor GCs is twenty times higher than the metal-rich GCs with respect to 
field stars. We find that a gradual increase in formation efficiency of GCs
with respect to field stars would be required with decreasing metallicity for
the GC candidates in the Auriga simulations to yield sufficient total mass to
be consistent with the MW or M31 GCS. In addition, the metal-poor GC candidates
would have to experience low mass los rates, especially those within the Solar
radius.

>>>>

\subsection{Radial distribution}
\label{sec:Rgc}
The bottom panel of Figure~\ref{fig:MW-M31-age-Rgc} shows the radial distribution
of the MW and M31 GCS. We divide the radii of M31 by its virial radius\footnote{
$r_{\text{vir}}$ is the radius in a spherical `top-hat' perturbation model at which
the average density reaches an overdensity of $\Delta_{\text{vir}}=357$ times the 
background density} $r_{\text{vir,M31}} = 299$~kpc and multiply by 
$r_{\text{vir,MW}} = 261$~kpc to account for the different intrinsic sizes of both 
galaxies, adopting the values and cosmology from \citet{2017MNRAS.464.3825P}.
Values for $r_{\text{gal}}$ are readily available in H96e10 (assuming $r_{\odot}=8.0$~kpc), 
but the galactocentric radius of GCs in M31 is not available in CR16. Therefore, we 
follow \citet[][section~4.1]{2019arXiv190111229W} 
to calculate the projected radius $r_{\text{proj}}$ from the observed positions,
adopting M31's central position from the NASA Extragalactic 
Database\footnote{\url{https://ned.ipac.caltech.edu/}} $(\alpha_0, \, \delta_0) =
(0^{\text{h}}42^{\text{m}}44.35^{\text{s}}, \, +41^{\circ}16'08.63")$
and distance $D_{\text{M31}} = 780$~kpc \citep{2005MNRAS.356..979M,2012ApJ...758...11C}.
We calculate $r_{\text{gal}}$ as `average deprojected distance`
$r_{\text{gal}} = r_{\text{proj}} \times (4/\pi)$.

@@

\subsection{Metallicity distribution}
\label{sec:results_FeH}
We investigate whether the star formation model implemented in Auriga produces 
metallicity distributions consistent with the MW and M31 GCSs, and whether
the simulations generate sufficient total mass at metallicities typical for the
MW and M31 GCSs. To visually inspect the former we show the normalized metallicity 
distribution of three specific Auriga galaxies in Figure~\ref{fig:Au4-10and21_FeH}
in comparison to the MW and M31 [Fe/H] distributions.

\begin{figure}
    \includegraphics[width=\columnwidth]{{FeH_obs_Au4-4_Au4-10_Au4-21}.png}
    \caption{
        \emph{Top}: Metallicity distribution of the MW and M31 GCS. The solid 
        purple (magenta) line shows the GCSs of the MW (M31), and we 
        indicate the mean value with an arrow at the bottom of the x-axis. We
        overplot a double Gaussian for the MW GCS using purple dotted lines, taking
        the mean and dispersion from \citep{Harris2001}.
        \emph{Other panels}: three selected Auriga haloes as indicated in the 
        upper right corner. In each of these three panels we show the GG 
        candidates in green, and use a green dotted line for all star particles. 
        We split the GC candidates up into two subpopulations, those that have 
        formed {\it in~situ} (blue), and those that have been accreted (red).
        \label{fig:Au4-10and21_FeH}
    }
\end{figure}
We select \mbox{Au4-10}\footnote{The nomenclature is `Au' for Auriga, followed by the
resolution level (4) and halo number (10, indicating which set of initial
conditions was used).}, \mbox{Au4-21}, and \mbox{Au4-4} to show the
distributions of three individual simulation runs that we consider representative
for specific behaviour, and to highlight that different runs could give rise to 
different distributions. We show the age-selected GC candidates as well as the 
accreted and {\it in~situ} subsets. The top panel of Figure~\ref{fig:Au4-10and21_FeH} shows the MW 
and M31 GCSs, where we overplot a double Gaussian for the MW GCS by 
adopting literature values of the mean $\mu$ and standard deviation $\sigma$ of 
the metal-rich and metal-poor subpopulations \citep{Harris2001}.

@@

To ease this comparison between the simulations and observations we take the ratio
of the total mass of GC candidates in Auriga to the total GC mass in the MW 
(and M31). We use a diverging colour map centered around the overall median of the 
mass ratio (i.e. we subtract the median of these twenty-five bins from the value 
in each bin). We show this in the top (bottom) panel of Figure~\ref{fig:Au-FeHRgc-ratio}.
Note that the data in the three top right bins is masked because the mass ratio cannot 
be calculated due to zero mass in the observations (therefore the bins are white).
If the product of the bound cluster formation efficiency and consecutive GC 
disruption over a Hubble time would be constant, then the value in each bin would
have been zero. The red and blue bins indicate deviations from such a scenario and
indicate a higher and lower than average mass excess in the simulations. The median 
value used to shift the mass ratio is $2.68$ and $1.69$ dex for the MW and M31, 
respectively. This means that the median `mass budget' that the simulations `can 
afford to lose' is roughly a factor $480$ and $50$ for the MW and M31, respectively. 
The lowest mass surplus for both galaxies is the bin where $-2.5 <$ [Fe/H] 
$< -1.5$ and $3 < r_{\text{gal}}/\text{kpc} < 8$, for which the simulations produce 
a factor $10^{2.68}/10^{1.33} \approx 22$ and $10^{1.69}/10^{0.75} \approx 9$ 
more mass in GC candidates than what is observed in the MW and M31 respectively.
The highest factor for the MW is $2.1 \times 10^{5}$, and $1.1 \times 10^{3}$
for M31.

@@

Finally, we note that \citet{2006ARA&A..44..193B} compares the number of metal-poor 
GCs to the stellar halo mass and find\footnote{The quantity $T$ is the number of 
GCs per $10^9$ M\Sun \, of galaxy stellar mass.} $T^n_{\text{blue}} \sim 100$, 
while the number of metal-rich GCs compared to the bulge mass yields 
$T^n_{\text{red}} \sim 5$, and therefore conclude that the formation efficiency
of metal-poor GCs is twenty times higher than the metal-rich GCs with respect to 
field stars. We find that a gradual increase in formation efficiency of GCs
with respect to field stars would be required with decreasing metallicity for
the GC candidates in the Auriga simulations to yield sufficient total mass to
be consistent with the MW or M31 GCS. In addition, the metal-poor GC candidates
would have to experience low mass loss rates, especially those within the Solar
radius.
